---
title: "Validation Report for Demo Environment Validation"
author: "Eli Miller"
date: "`r Sys.Date()`"
output:
  pdf_document: 
    toc: yes
    fig_crop: no
    toc_depth: 2
    number_sections: yes
vignette: |
  %\VignetteIndexEntry{Validation Report} \usepackage[utf8]{inputenc} %\VignetteEngine{knitr::rmarkdown_notangle}
header-includes:
- \usepackage{array}
- \usepackage{float}
- \usepackage{multirow}
- \usepackage{longtable}
- \usepackage{booktabs}
- \usepackage{xcolor}
always_allow_html: yes
---


```{r, setup, echo=FALSE,warning=FALSE}
suppressPackageStartupMessages({
  library(valtools)
  library(knitr)
  library(kableExtra)
  library(magrittr)
  library(devtools)
  library(tools)
  library(stringr)
  library(dplyr)
  library(riskmetric)
  library(renv)
  library(testthat)
})

opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = TRUE,
  echo = FALSE,
  results = "asis",
  message = FALSE,
  tidy = FALSE,
  rmarkdown.pandoc.to = "latex"
)

options(
  knitr.kable.NA = '',
  knitr.duplicate.label = "allow"
)

```


\newpage

# Release details

## Package Information

### Change Log

```{r change-log-table}
vt_scrape_change_log() %>% 
  vt_kable_change_log()
```

### Validation Environment

```{r env-table}
vt_scrape_val_env() %>%
  vt_kable_val_env()
```

\clearpage

## Authors

### Requirements 


```{r req-authors}
vt_scrape_requirement_editors() %>% 
  vt_kable_requirement_editors()
```

### Test Case Authors

```{r test-case-authors}
vt_scrape_test_case_editors() %>%
 vt_kable_test_case_editors()
```

### Test Code Authors

```{r test-code-authors}
vt_scrape_test_code_editors() %>%
 vt_kable_test_code_editors()
```

## Traceability

```{r traceability, fig.width=20}
## TODO: Make figure wider
vt_scrape_coverage_matrix() %>% 
 vt_kable_coverage_matrix()
```

\clearpage

# Risk Assessment

## Requirement Assessments

```{r risk}
vt_scrape_risk_assessment() %>% 
  vt_kable_risk_assessment()
```

## Package Assessments

This table displays the riskmetric score of the `dplyr` and `Tplyr` packages. Other packages can be added as needed.

```{r riskmetric}
scores <- c("Tplyr", "dplyr") %>%
  pkg_ref() %>%
  pkg_assess() %>%
  pkg_score() %>%
  summarize_scores()

df <-   data.frame(
    Package = c("Tplyr", "dplyr"),
  "riskmetric Scores" = scores)

t <- kable(
  df,
  longtable = TRUE)
t <- column_spec(t, 1, border_left = TRUE)
t <- column_spec(t, ncol(df), border_right = TRUE)
t <- collapse_rows(t, c(1))
t <- kable_styling(t, latex_options = "hold_position")
t

```

\clearpage

# Validation

```{r child-files-evaluation}
df <- data.frame(
  x = c("requirements", "test_cases", "test_code"),
  y = c("requirements.md", "cases.md", "tests.R")
)
child_files <- vt_get_child_files() %>%
  str_split("/", simplify = TRUE) %>%
  as.data.frame() %>%
  arrange(V2) %>%
  mutate(V1 = factor(V1, c("requirements", "test_cases", "test_code"))) %>%
  filter(V2 != "_snaps") %>%
  left_join(df, by = c(V1 = "x"))
ch_files <- paste(child_files$V1, child_files$V2, child_files$y, sep = "/")
vt_file(vt_path(ch_files),dynamic_referencing = FALSE)
```
## Installed System Packages
```md
```{r, installed-packages, results='asis'}
cat(renv::diagnostics())
```
```
